On Secure Delegation of SampBQP with a Classical Client

### 2020-03-23 blind.tex
Simplify blindness compiler

	Let $L_t$ be the circuit depth of $\cP_t$.
	Let $\lambda=\abs{x}$.

	\begin{enumerate}
		\item $\Vblind$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(x)$.
			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$,
			and encrypts $\ctx{x}{}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
			It sends $pk_1$, $\ctx{x}{}{1}$, and $\ctx{v}{1}{1}$ to the prover.
		\item $\Pblind$ generates $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(\ctx{v}{1}{1}, \ctx{x}{}{1})$
			by evaluating $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\QEval_{pk}(\cP_1, \ctx{v}{1}{1}, \ctx{x}{}{1})$.
			It sends $\ctx{p}{1}{1}$ to the verifier.
		\item for $t=2,\ldots,T$:
		\begin{enumerate}
			\item $\Vblind$ decrypts the prover's last message by $p_{t-1}\leftarrow\QDec_{sk_{t-1}}(\ctx{p}{t-1}{t-1})$,
				then generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$,
				and produces encryptions $\ctx{v}{t}{t}\leftarrow\QEnc_{pk_t}(v_t)$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
				It sends $pk_t$, $\ctx{v}{t}{t}$, and $\ctx{sk}{t-1}{t}$ to the prover.
			\item $\Pblind$ generates $(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\cPblind{t}(\ctx{v}{t}{t}, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1})$
				by first switching the $\QHE$ key that its states is encrypted under;
				that is, it first encrypts it under the new key by $\ctx{st}{P, t-1}{t-1, t}\leftarrow\QEnc_{pk_t}(\ctx{st}{P, t-1}{t-1}))$,
				then homomorphically decrypting the old encryption under the new key by
				$\ctx{st}{P, t-1}{t}\leftarrow\QEval_{pk_t}(\QDec, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t})$.
				It then applies the next-message function of $\Pi$ homomorphically, generating
				$(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\QEval_{pk_t}(\cP_t, \ctx{v}{t}{t}, \ctx{st}{P, t-1}{t})$.
				It sends $\ctx{p}{t}{t}$ back to the verifier.
		\end{enumerate}
		\item $\Vblind$ decrypts the prover's final message by $p_T\leftarrow\QDec_{sk_T}(\ctx{p}{T}{T})$.
			It then computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
	\end{enumerate}
\end{protocol}

@@

	On $\cPstar{1}$ it generates
	$(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^{L_1})$, then produces the encryptions
	$\ctx{x}{}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
	It then runs $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(\ctx{v}{1}{1}, \ctx{x}{}{1})$.
	Finally, it decrypts $p_1\leftarrow\QDec_{sk_1}(\ctx{p}{1}{1})$ and sends it back to the verifier,
	and keeps $\ctx{st}{P, 1}{1}$ and $sk_1$.

	Then, on the rest of the $\cPstar{t}$ rounds, it generates
	$(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^{L_t})$, and produces ciphertexts
	$\ctx{v}{t}{t}\leftarrow\QEnc_{pk_t}(v_t))$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
	It then runs $(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\cPblind{t}(\ctx{v}{t}{t}, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1})$.
	Finally, it decrypts $p_t\leftarrow\QDec_{sk_t}(\ctx{p}{t}{1})$ and sends it back to the verifier,
	and keeps $\ctx{st}{P, t}{t}$ and $sk_t$.

>>>>

	Let $L=\poly(x)$, $\lambda=\poly(x)$.

	\begin{enumerate}
		\item $\Vblind$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(x)$.
			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^L)$,
			and encrypts $\ctx{x}{}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
			It sends $pk_1$, $\ctx{x}{}{1}$, and $\ctx{v}{1}{1}$ to the prover.
		\item $\Pblind$ generates $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(\ctx{v}{1}{1}, \ctx{x}{}{1})$
			by evaluating $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\QEval_{pk}(\cP_1, \ctx{v}{1}{1}, \ctx{x}{}{1})$.
			It sends $\ctx{p}{1}{1}$ to the verifier.
		\item for $t=2,\ldots,T$:
		\begin{enumerate}
			\item $\Vblind$ decrypts the prover's last message by $p_{t-1}\leftarrow\QDec_{sk_{t-1}}(\ctx{p}{t-1}{t-1})$,
				then generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^L)$,
				and produces encryptions $\ctx{v}{t}{t}\leftarrow\QEnc_{pk_t}(v_t)$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
				It sends $pk_t$, $\ctx{v}{t}{t}$, and $\ctx{sk}{t-1}{t}$ to the prover.
			\item $\Pblind$ generates $(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\cPblind{t}(\ctx{v}{t}{t}, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1})$
				by first switching its encryption key;
				that is, it encrypts its state under the new key by $\ctx{st}{P, t-1}{t-1, t}\leftarrow\QEnc_{pk_t}(\ctx{st}{P, t-1}{t-1}))$,
				then homomorphically decrypts the old encryption by
				$\ctx{st}{P, t-1}{t}\leftarrow\QEval_{pk_t}(\QDec, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t})$.
				Then it applies the next-message function of $\Pi$ homomorphically, generating
				$(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\QEval_{pk_t}(\cP_t, \ctx{v}{t}{t}, \ctx{st}{P, t-1}{t})$.
				It sends $\ctx{p}{t}{t}$ back to the verifier.
		\end{enumerate}
		\item $\Vblind$ decrypts the prover's final message by $p_T\leftarrow\QDec_{sk_T}(\ctx{p}{T}{T})$.
			It then computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
	\end{enumerate}
\end{protocol}

@@

	On $\cPstar{1}$ it generates
	$(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^L)$, then produces the encryptions
	$\ctx{x}{}{1}\leftarrow\QEnc_{pk_1}(x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc_{pk_1}(v_1)$.
	It then runs $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(\ctx{v}{1}{1}, \ctx{x}{}{1})$.
	Finally, it decrypts $p_1\leftarrow\QDec_{sk_1}(\ctx{p}{1}{1})$ and sends it back to the verifier,
	and keeps $\ctx{st}{P, 1}{1}$ and $sk_1$.

	Then, on the rest of the $\cPstar{t}$ rounds, it generates
	$(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^L)$, and produces ciphertexts
	$\ctx{v}{t}{t}\leftarrow\QEnc_{pk_t}(v_t))$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc_{pk_t}(sk_{t-1})$.
	It then runs $(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\cPblind{t}(\ctx{v}{t}{t}, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1})$.
	Finally, it decrypts $p_t\leftarrow\QDec_{sk_t}(\ctx{p}{t}{1})$ and sends it back to the verifier,
	and keeps $\ctx{st}{P, t}{t}$ and $sk_t$.
